### 2014-03-15 HowtoHowtoCapon/submission/submit1/answer/answer.tex
la2pdf commit - 2014:03:15	15:17:09	(Sat15.Mar)
la2pdf commit - 2014:03:15	15:48:34	(Sat15.Mar)

\ai{This is a good point. The Oxford dictionary lists "MP" as the correct abbreviation for "megapixel", so we substituted "Mpx/s" with "MP/s" and included a proper definition.}

@@

\ai{Thank you, we were not aware of this. Corrections applied.}

@@

\ai{You are right that subarray averaging is important in our study. But we believe that "subarray MVDR" would be misleading, as our use of subarrays is strictly due to the application of MVDR in an active system to decorrelate signal and interference. TODO: Citation }

@@

\ai{Thank you. Corrected.}

>>>>

\ai{This is a good point. "Mpx" is now corrected to "MP", in accordance with the second reviewer's suggestion and the Oxford dictionary.}

@@

\ai{Thank you, we agree. Corrections applied.}

@@

\ai{You are right that subarray averaging is important in our study. But we believe that "subarray MVDR" would be misleading, as we use subarray averaging mainly to deal with the coherent echoes in active sonar. We have now stated this better up front in the article.}

@@

\ai{We thank the reviewer for these corrections (8.-10.). Corrections applied.}
